\documentclass{aastex63}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage{xspace}

\usepackage{graphicx}

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

\let\oldAA\AA
\renewcommand{\AA}{\text{\normalfont\oldAA}}
% cmds for this paper 
\newcommand{\gr}{g{-}r}
\newcommand{\fnuv}{FUV{-}NUV}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\ssfr}{{\rm SSFR}}
\newcommand{\mtaum}{m_{\tau,M_*}}
\newcommand{\mtaus}{m_{\tau,{\rm SSFR}}}
\newcommand{\ctau}{c_\tau}
\newcommand{\mdeltam}{m_{\delta,M_*}}
\newcommand{\mdeltas}{m_{\delta,{\rm SFR}}}
\newcommand{\cdelta}{c_\delta}
\newcommand{\eda}{EDA}


\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\ch}[1]{#1}%{\color{orange}#1}}
\newcommand{\chedit}[1]{{\color{orange}#1}}
\newcommand{\tks}[1]{{\color{blue}#1}}
\newcommand{\tksedit}[1]{{\color{blue}#1}}

\shorttitle{The Empirical Dust Attenuation Framework}
\shortauthors{Hahn et al.}


\begin{document} 

\title{IQ Collaboratory III: The Empirical Dust Attenuation Framework ---
Taking Hydrodynamical Simulations with a Grain of Dust}

\author[0000-0003-1197-0902]{ChangHoon Hahn}
\correspondingauthor{ChangHoon Hahn}
\email{changhoon.hahn@princeton.edu}
\affil{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544, USA} 

\author{Tjitske K. Starkenburg}
\affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and \\Department of Physics and Astronomy, 1800 Sherman Ave, Evanston IL 60201, USA}

\author{Daniel Angl\'es-Alc\'azar}
\affil{Department of Physics, University of Connecticut, 196 Auditorium Road,
U-3046, Storrs, CT 06269-3046, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave,
New York, NY 10010, USA}

\author[0000-0002-8131-6378]{Ena Choi}
\affil{Quantum Universe Center, 
        Korea Institute for Advanced Study, 
        Hoegiro 85, Seoul 02455, Korea}

\author{Romeel Dav\'e}
\affil{Institute for Astronomy, Royal Observatory, Univ. of Edinburgh, Edinburgh EH9 3HJ, UK}
\affil{University of the Western Cape, Bellville, Cape Town 7535, South Africa}
\affil{South African Astronomical Observatories, Observatory, Cape Town 7925, South Africa}

\author[0000-0002-1081-3991]{Claire Dickey} 
\affil{Department of Astronomy, Yale University, New Haven CT 06520 USA}

%\suppressAffiliations
\author[0000-0001-9298-3523]{Kartheik G. Iyer}
\affil{Dunlap Institute for Astronomy and Astrophysics, University of Toronto,
50 St George St, Toronto, ON M5S 3H4, Canada}

\author[0000-0003-2060-8331]{Ariyeh H. Maller}
\affil{Department of Physics, New York City College of Technology, City
University of New York, 300 Jay St., Brooklyn, NY 11201, USA}

\author{Rachel S. Somerville}
\affil{Department of Physics and Astronomy, Rutgers University, 136
Frelinghuysen Road, Piscataway, NJ 08854, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave,
New York, NY 10010, USA}

\author{Jeremy L. Tinker}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}

\author{L. Y. Aaron Yung}
\affil{Astrophysics Science Division, NASA Goddard Space Flight Center, 8800 Greenbelt Rd, Greenbelt, MD 20771, USA}

%\collaboration{2}{IQ Collaboratory}

%\AuthorCallLimit=3

\begin{abstract}
    We present the Empirical Dust Attenuation (\eda) framework --- a flexible
    prescription for 
    %for applying dust attenuation to galaxies from theoretical models. \eda~provides a flexible prescription 
    assigning realistic dust attenuation to simulated galaxies based on their
    physical properties. % ($M_*$, $\ssfr$). %  and using the \cite{noll2009} attenuation curve parameterization. 
    We use the \eda~to forward model synthetic observations for three state-of-the-art large-scale cosmological
    hydrodynamical simulations: SIMBA, IllustrisTNG, and EAGLE. 
    We then compare the optical
    and UV color-magnitude relations, $(\gr) - M_r$ and $(\fnuv)-M_r$, of the
    simulations to a $M_r < -20$ complete SDSS galaxy sample using
    likelihood-free inference. 
    Without dust, none of the simulations match observations, as expected.
    %As expected, the simulations cannot match observations without dust. % for all three simulations, dust attenuation is {\em necessary} to match the observations.
    With the \eda, however, we can reproduce the observed color-magnitude
    with all three simulations. 
    %For SIMBA and TNG, we find an excess of luminous UV-red galaxies that dust cannot fix because the simulations quench star formation too efficiently in the most massive galaxies. 
    Furthermore, the attenuation curves predicted by our dust prescription are
    in good agreement with the observed attenuation--slope relations and
    attenuation curves of star-forming galaxies. 
    However, the \eda~does not predict star-forming galaxies with low
    $A_V$ since simulated star-forming galaxies are intrinsically much
    brighter than observations.
    Additionally, the \eda~provides, for the first time, predictions
    on the attenuation curves of quiescent galaxies, which are challenging to
    measure observationally. 
    Simulated quiescent galaxies require shallower attenuation curves
    with lower amplitude than star-forming galaxies.
    %Overall, we find that more massive galaxies in the simulations require higher dust attenuation, while galaxies with higher specific star formation rates have steeper attenuation curves.
    The \eda, combined with forward modeling, provides an effective
    approach for shedding light on  dust in galaxies and
    probing hydrodynamical simulations. 
    This work also illustrates a major limitation in comparing galaxy
    formation models: by adjusting dust attenuation, simulations that predict
    significantly different galaxy populations can reproduce the same UV
    and optical observations. 
\end{abstract}

\keywords{
    galaxies: formation -- galaxies: evolution -- galaxies: statistics -- methods: numerical 
}
\NewPageAfterKeywords

% --- intro ---  
\input{intro}
% --- data ---  
\input{sims} 
% --- methods ---  
\input{dem}

\input{abc}
% --- results ---  
\input{results}
% --- summary ---  
\input{summary}

\section*{Acknowledgements}
It's a pleasure to thank 
    Michael Blanton, 
    Nicholas T. Faucher, 
    Marla Geha, 
    Shy Genel,
    Jenny E. Green,
    Daniel Kelson, 
    Mariska Kriek, 
    Peter Melchior, 
    Desika Narayanan, 
    Samir Salim, 
    and Katherine Suess for
valuable discussions and comments.
This material is based upon work supported by the U.S. Department of Energy,
Office of Science, Office of High Energy Physics, under contract No.
DE-AC02-05CH11231. 
CH is supported by the AI Accelerator program of the Schmidt Futures Foundation.

We thank the Illustris collaboration and the Virgo Consortium for making their
simulation data publicly available, and the SIMBA collaboration for sharing
their data with us.
The EAGLE and SIMBA simulations were performed using the DiRAC-2 facility at
Durham, managed by the ICC, and the PRACE facility Curie based in France at
TGCC, CEA, Bruy\`{e}res-le-Ch\^{a}tel.

This research was supported in part through the computational resources and
staff contributions provided by the Quest high performance computing facility
at Northwestern University, which is jointly supported by the Office of the
Provost, the Office for Research, and Northwestern University Information
Technology. 

The data used in this work were, in part, hosted on facilities supported by the
Scientific Computing Core at the Flatiron Institute, a division of the Simons
Foundation, and the analysis was largely done using those facilities.
The IQ~(Isolated \& Quiescent)~Collaboratory thanks the Flatiron Institute for hosting the collaboratory and its meetings. 
The Flatiron Institute is supported by the Simons Foundation.
Funding for the Sloan Digital Sky Survey IV has been provided by the Alfred P.
Sloan Foundation, the U.S. Department of Energy Office of Science, and the
Participating Institutions. SDSS acknowledges support and resources from the
Center for High-Performance Computing at the University of Utah. The SDSS web
site is www.sdss.org.
The SDSS is managed by the Astrophysical Research Consortium for the
Participating Institutions.

\appendix
%\input{unc.tex}
%\input{res.tex} 
\input{slab.tex} 


\bibliographystyle{mnras}
\bibliography{galpopfm} 

\allauthors
\end{document}
